A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-03-15 main.tex
Updates from Overleaf

In personal history section of admission note for inpatient:\\
<Habits>\\
-Tobacco: __ pack/day for __ years\\
-Alcohol drinking: Occasionally\\
-Betel nuts: __ nuts/day for __ years\\
<Social/Economic Evaluation>\\
-Living condition: Living with family\\
-Family support: Well\\
-Main caregiver: Spouse\\
-Financial support: Sufficient\\
<Psychological Evaluation>\\
Stable but worry about this oral lesion\\
Suspected to be abuse or neglected victim: negative\\
<Spiritual Assessment>\\
Religion: Nil\\
Diagnosed with life-threatening diseases or terminal stage of chronic diseases or cancers? No\\
% cancer cure (care) 的證明
%# 懺悔
We continually educate our cancer patients that they should repentantly confess for not taking care of body and spirit in the past, and sincere thanks for our physical body does hard work. Mindfulness and meditation will be helpful in cancer healthcare.
Once the holistic feature is available, a graph convolutional neural network (GCNN) is mandatory for further survival analysis\cite{Ching2018a}.
The microenvironment of HNSCC, influenced by the mind-brain-body axis, requires further exploration and understanding using this multi-parametric approach.
%  extreme pleasure, anger, overthinking, sadness, fear, shock, anxiety, depression, fatigue, stress
%七情: 喜、怒、思、悲、恐、驚、憂

>>>>

In personal history section of admission note for inpatient:\\
<Habits>\\
-Tobacco: \underline{ }\underline{ } pack/day for \underline{ }\underline{ } years\\
-Alcohol drinking: Occasionally\\
-Betel nuts: \underline{ }\underline{ } nuts/day for \underline{ }\underline{ } years\\
<Social/Economic Evaluation>\\
-Living condition: Living with family\\
-Family support: Well\\
-Main caregiver: Spouse\\
-Financial support: Sufficient\\
<Psychological Evaluation>\\
Stable but worry about this oral lesion\\
Suspected to be abuse or neglected victim: negative\\
<Spiritual Assessment>\\
Religion: Nil\\
Diagnosed with life-threatening diseases or terminal stage of chronic diseases or cancers? No\\
% cancer cure (care) 的證明
%# 懺悔
We continually educate our cancer patients that they should repentantly confess for not taking care of body and spirit in the past, and sincere thanks for our physical body does hard work. Mindfulness and meditation will be helpful in cancer healthcare.
Once the holistic feature is available, a graph convolutional neural network (GCNN) is mandatory for further survival analysis\cite{Ching2018a}.
The microenvironment of HNSCC, influenced by the mind-brain-body axis, requires further exploration and understanding using this multi-parametric approach.
%  extreme pleasure, anger, overthinking, sadness, fear, shock, anxiety, depression, fatigue, stress
%七情: 喜、怒、思、悲、恐、驚、憂
